Critical Temperature of YBCO and BSCCO Superconductors

### 2014-11-26 Draft.tex
fixed images in paper

\begin{figure}[width=5in][h!]
\centering
\includegraphics{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

@@

\begin{figure}[width=5in][h!]
\centering
\includegraphics{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[width=5in][h!]
\centering
\includegraphics{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

@@

\begin{figure}[width=10mm][h!]
\centering
\includegraphics{bscco_resistance_vs_temperature.png}
\caption{Plot of resistance vs temperature for BSCCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.}
\label{BSCCOplot1}
\end{figure}

\begin{figure}[width=3in][h!]
\centering
\includegraphics{bscco_superconductivity_close-up.png}
\caption{Close up of the BSCCO sample warm-up during it superconductive phase. Irregularities are definitely present, but jumps are not clear.}
\label{BSCCOplot2}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{bscco_resistance_vs_temperature.png}
\caption{Plot of resistance vs temperature for BSCCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between.}
\label{BSCCOplot1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{bscco_superconductivity_close-up.png}
\caption{Close up of the BSCCO sample warm-up during it superconductive phase. Irregularities are definitely present, but jumps are not clear.}
\label{BSCCOplot2}
\end{figure}
